\chapter*{Revision History}
\begin{center}
    \begin{tabularx}{\textwidth}{ | l | l | X | l | }
        \hline
        \textbf{Version}  & \textbf{Date}  & \textbf{Description}                                                    & \textbf{Authors} \\\hline
        0.1               & 8 March 2020   & Designed a prototype of the general layout of the document              & R. Voetman J. Mellema \\\hline
        1.0               & 10 March 2020  & Wrote the basic structure for the preface.                              & J. Mellema \\\hline
        1.1               & 11 March 2020  & General layout complies with the standards prescribed by the University & J. Mellema \\\hline
        1.2               & 14 March 2020  & Enhanced layout by converting the document to the LaTeX file format. & R. Voetman \\\hline
        1.3               & 15 March 2020  & Wrote the problem identification & R. Voetman \\\hline
        1.4               & 17 March 2020  & Wrote the Introduction & J. Mellema \\\hline
        1.5               & 18 March 2020  & Defined the problem statement, objective and research questions. & R. Voetman J. Mellema \\\hline
        1.6               & 18 March 2020  & Defined the concept “Ethical software development” in the theoretical framework. & R. Voetman \\\hline
        1.7               & 21 March 2020  & Conducted and composed the Ethical Analysis  & R. Voetman \\\hline
        1.8               & 21 March 2020  & Elaborated on the concept of “Weak Artificial Intelligence”, defined a definition which will be used in this report. & J. Mellema \\\hline
        1.9               & 23 March 2020  & Conducted the technical analysis, removed some IT jargon, rewrote the introduction and the problem characterization. & J. Mellema \\\hline
        1.10               & 25 March 2020  & Concluded the analysis which serves as a basis for the recommendation. & R. Voetman J. Mellema \\\hline
        1.11               & 26 March 2020  & Formatted the bibliography in LaTeX format. & J. Mellema \\\hline
        1.12               & 27 March 2020  & Formatted the Bibliography using APA-style formatting. Ensured that the report will comply to the international standard. & R. Voetman J. Mellema \\\hline

    \end{tabularx}
\end{center}